\section{PUBLICATIONS}

\begin{itemize}
\setlength\itemsep{5pt}
    \item Hupkes D., Rodriguez Luna D., Ponti E.M. and Bruni E. Internal and External Pressures on Language Emergence:
Least Effort, Object Constancy and Frequency. \textit{In prep}.
    \item Dagan, G., Hupkes, D. and Bruni E. Co-evolution of language and agent. \textit{In prep.}
    \item Hupkes D., Dankers V., Mul M. and Bruni E. \href{https://arxiv.org/pdf/1908.08351.pdf}{The compositionality of neural networks: integrating symbolism and connectionism}. \textit{Accepted for publication in JAIR.}
    
    \item Jumelet J., Zuidema W. and Hupkes D. (2019). \href{https://arxiv.org/pdf/1909.08975.pdf}{Analysing Neural Language Models: Contextual Decomposition Reveals Default Reasoning in Number and Gender Assignment}. \textit{CONLL 2019}.
    
    \item Baan J., Leible J., Nikolaus M., Rau D., Ulmer D., Baumgärtner T., Hupkes D. and Bruni E. (2019). \href{https://www.aclweb.org/anthology/W19-4814}{On the Realization of Compositionality in Neural Networks}. \textit{BlackboxNLP, ACL 2019}. 
    
    \item Ulmer D., Hupkes, D. and Bruni, E (2019). \href{https://www.aclweb.org/anthology/W19-4324}{Assessing incrementality in sequence-to-sequence models}. \textit{Repl4NLP, ACL 2019}. 
    
    \item Korrel K., Hupkes D., Dankers V., and Bruni E. (2019) \href{https://www.aclweb.org/anthology/W19-4801}{Transcoding compositionally: using attention to find more generalizable solutions}. \textit{BlackboxNLP, ACL 2019}.
    
    \item Lakretz Y., Kruszewski G., Desbordes T., Hupkes D., Dehaene S. and Baroni M. (2019) \href{https://www.aclweb.org/anthology/N19-1002}{The emergence of number and syntax units in LSTM language models}. \textit{NAACL 2019}.

    \item  Hupkes D., Singh A.K., Korrel K., Kruszewski G. and, Bruni E (2019). \href{https://arxiv.org/abs/1805.09657}{Learning compositionally through attentive guidance}. \textit{CICLing 2019}.
    
    \item Leonandya R., Bruni E., Hupkes D. and Kruszewski G (2019). \href{https://www.aclweb.org/anthology/W19-0419/}{The Fast and the Flexible: training neural networks to learn to follow instructions from small data.} \textit{IWCS}. 
    
    \item Hupkes D., Veldhoen S., and Zuidema W. (2018). \href{https://jair.org/index.php/jair/article/view/11196/26408}{Visualisation and ‘diagnostic classifiers’ reveal how recurrent and recursive neural networks process hierarchical structure}. \textit{Journal of Artificial Intelligence Research}.
    
    \item Giulianelli, M., Harding, J., Mohnert, F., Hupkes, D. and Zuidema, W. (2018). \href{https://aclweb.org/anthology/W18-5426}{Under the hood: using diagnostic classifiers to investigate and improve how language models track agreement information.} \textit{BlackboxNLP 2018, ACL}. \\ \textbf{Best paper award}.
    
    \item Zuidema W., Hupkes D., Wiggins G., Scharf C. and Rohrmeier M. (2018). Formal models of \href{https://arxiv.org/abs/1901.05180}{Structure Building in Music, Language and Animal Song}. In \textit{The Origins of Musicality}.
    
    \item Jumelet, J. and Hupkes, D. (2018). \href{https://aclweb.org/anthology/W18-5424}{Do language models understand anything? On the ability of LSTMs to understand negative polarity items}. \textit{BlackboxNLP 2018, ACL}.
    
    \item Hupkes, D., Bouwmeester, S. and Fernández, R. (2018). \href{https://aclweb.org/anthology/W18-5419}{Analysing the potential of seq2seq models for incremental interpretation in task-oriented dialogue}. \textit{BlackboxNLP 2018, ACL}.
    
    \item Hupkes D. and Zuidema W. (2017) \href{http://www.interpretable-ml.org/nips2017workshop/papers/12.pdf}{Diagnostic classification and symbolic guidance to understand and improve recurrent neural networks}. \textit{Interpreting, Explaining and Visualizing Deep Learning, NIPS2017}.
    
    \item Veldhoen S., Hupkes D. and Zuidema W. (2016). \href{http://dieuwkehupkes.nl/research/nips2016.pdf}{Diagnostic Classifiers: Revealing how Neural
Networks Process Hierarchical Shructure}. \textit{Cognitive Computation: Integrating Neural and
Symbolic Approaches, NIPS2016}.

    \item Hupkes D. and Bod R (2016) \href{https://www.aclweb.org/anthology/L16-1012}{POS-tagging of Historical Dutch}. \textit{LREC2016}.
\end{itemize}
