\section{TALKS \& PANELS}

\begin{itemize}
    \setlength\itemsep{5pt}
    \item \textit{March 17, 2021}, Kunnen we kunstmatige intelligentie nog doorgronden? Studium Generale, \textit{Utrecht} (virtual talk)
    \item \textit{February 11, 2021}, Compositionality decomposed: how do neural networks generalise? Women@CL, \textit{University of Cambridge} (virtual talk)
    \item \textit{February 5, 2021}, Compositionality decomposed: how about natural data? \textit{Rijksuniversiteit Groningen} (virtual talk)
        \item \textit{August}. TBA. Keynote speaker at the workshop Computational and experimental explanations in semantics and pragmatics, \textit{Utrecht}. \textcolor{red}{ -- Post-poned because of COVID19}
        \item \textit{November}. TBA. Keynote speaker at EurNLP, \textit{Paris}. \textcolor{red}{ -- Post-poned because of COVID19}
    \item \textit{October 31, 2020}, Neural networks as explanatory models of language processing, ILCC Seminar at the University of Edinburgh, \textit{Edinburgh} (virtual talk)
    \item \textit{September 17, 2020}, Neural networks as explanatory models, AllenNLP, \textit{Seattle} (virtual talk)
    \item \textit{November 15, 2019}. Syntax in neural language models: a case study \textit{University of Utrecht, Utrecht}
    \item \textit{October 9, 2019}. Subject verb agreement in neural language models -- how, when and where? \textit{Johns Hopkins University, Baltimore}
    \item \textit{October 1, 2019}. What do they learn? Neural networks, compositionality and interpretability. \textit{Computational Cognition workshop, Osnabruek}.
    \item \textit{September 3, 2019}. Guest speaker and panelist at the public event When fake looks all too real: the technology behind Deep Fake, \textit{SPUI25, Amsterdam}.
    \item \textit{August 1, 2019}. Blackbox NLP, \textbf{panel moderator}.
    \item \textit{June 18, 2019}. The typology of emergent languages. \textit{Interaction and the Evolution of Linguistic Complexity, Edinburgh}.
    \item \textit{May 6.} The compositionality of neural networks: integrating symbolism and connectionism. \textit{CS\&AI / SIKS workshop on analyzing and interpreting neural networks for NLP, ‘s-Hertogenbosch}.
    \item \textit{April 18}. The compositionality of neural networks: integrating symbolism and connectionism. \textit{Invited internal talk at Saarland University, Saarbrücken}.
    \item \textit{March 14}. On neural networks and compositionality. \textit{Invited internal seminar at École normale supérieure, Paris}.
    \item \textit{July 18, 2018}. Visualisation and ‘diagnostic classifiers’ reveal how recurrent and recursive neural networks process hierarchical structure. \textit{IJCAI, Stockholm}.
    \item \textit{June 12, 2018}. Learning compositionally through attentive guidance. \textit{Invited internal seminar at the University of Copenhagen.}
    \item \textit{May 9, 2017}. Processing hierarchical structure with RNNs.\textit{ Dagstuhl seminar on Human-like neural-symbolic computing.}
    \item \textit{December 7, 2017}. The grammar of neural networks. \textit{SMART workshop Grammars, Computation \& Cognition, Amsterdam.}
    \item \textit{December 15, 2017}. Hierarchical compositionality in recurrent neural networks. \textit{Invited internal seminar at Rijksuniversiteit Groningen.}
    \item \textit{May 25, 2016}. POS-tagging of Historical Dutch. \textit{LREC, Portoroz}.
    \item \textit{November 22, 2016}. How may neural networks process hierarchical structure? Insights from recursive and recurrent networks learning arithmetics. \textit{Logic Tea at the University of Amsterdam.}
    \item \textit{June 8, 2015} Using Parallel Data to improve Part-of-Speech tagging of 17th century Dutch. \textit{DH Benelux, Antwerp.}
\end{itemize}
